\bfseries \boldmath \scititle

### 2025-12-20 latex/main.tex
Updates from Overleaf
Basic compiling version of document

% Notes on format:
% The total word count of an article must be under 7,000 (including main figure
% legends but excluding STAR Methods text, supplemental item legends, and
% references section), and there should be no more than seven figures and/or
% tables.

\documentclass[12pt,letterpaper]{article}
\usepackage[a4paper, total={7in, 10in}]{geometry}
\renewcommand{\familydefault}{\sfdefault}
\usepackage{graphicx}
\usepackage{helvet}
\usepackage{authblk}
\usepackage[hypertexnames=false]{hyperref}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{placeins}
\usepackage{orcidlink}
\usepackage[super,comma,sort&compress]
   {natbib}\bibliographystyle{numbered}
\usepackage[right]{lineno} \linenumbers
\usepackage[normalem]{ulem}

\graphicspath{ {../figures/} }

\makeatletter
\renewcommand{\maketitle}{\bgroup\setlength{\parindent}{0pt}
\begin{flushleft}
  \textbf{\@title}

  \@author
\end{flushleft}\egroup}
\makeatother

%%%  Insert title below; leave date empty.

\title{A Pandemic-Scale Ancestral Recombination Graph for SARS-CoV-2}
\date{}

%%%  Author first and last names should be spelled
%%%  out in their entirety (do not abbreviate "J.H.
%%%  Watson" unless this is how the author's name
%%%  always appears). Middle initials are OK. Do
%%%  not include titles, positions, or degrees.

%%%  Use numbered footnotes to indicate institutional
%%%  affiliations. Authors may have multiple
%%%  institutional affiliations, and affiliations
%%%  may be shared among multiple authors.

%%%  After the institutional affiliations, numbered
%%%  footnotes may be used to indicate an author's
%%%  present address, equal contribution status,
%%%  and/or senior author status.

%%%  The final numbered footnote should indicate
%%%  which author is the lead contact (required).
%%%  One author must be designated as the lead contact.
%%%  There can be no more than one lead contact.

%%%  Corresponding authors should be indicated with
%%%  asterisks (*). Use 2 asterisks (**) for the
%%%  second-listed corresponding author, 3 (***) for
%%%  the third-listed, and so on. The lead contact
%%%  must be a corresponding author. Additional
%%%  authors may also serve as corresponding authors.

% \author[1,\orcidlink{0000-0000-0000-0000}]{First Last}
% \author[1,2]{First Middle Last}
% \author[2,3]{First M.M. Last}
% \author[3,*]{First Last, Jr.}
% \author[3,4,5,**]{F. Middle Last}

\author[1,2,8,*,\orcidlink{0000-0002-6351-8873}]{Shing~H.~Zhan}
\author[1,7,\orcidlink{0000-0002-3536-6411}]{Yan~Wong}
\author[3,7,\orcidlink{0000-0001-6402-9396}]{Anastasia~Ignatieva}
\author[4,\orcidlink{0000-0001-6862-7756}]{Katherine~Eaton}
\author[1,\orcidlink{0000-0002-3547-7226}]{Isobel~Guthrie}
\author[1,\orcidlink{0000-0002-1982-6801}]{Benjamin~Jeffery}
\author[1,3,5,\orcidlink{0000-0002-0824-0047}]{Duncan~S.~Palmer}
\author[4,\orcidlink{0000-0002-1543-4501}]{Carmen~Lia~Murall}
\author[6,\orcidlink{0000-0003-3042-0818}]{Sarah~P.~Otto}
\author[1,**,\orcidlink{0000-0002-7894-5253}]{Jerome~Kelleher}

%%%  Institutional affiliations should contain the
%%%  following information at minimum: department(s)/
%%%  subunit(s), institution, city, state/region (if
%%%  applicable), and country.

\affil[1]{Big Data Institute, Li Ka Shing Centre for Health
Information and Discovery, University of Oxford, United Kingdom}
\affil[2]{Infectious Disease Epidemiology Unit (IDEU), Nuffield Department of Population Health, University of Oxford, Oxford, United Kingdom}
\affil[3]{Department of Statistics, University of Oxford, United Kingdom}
\affil[4]{National Microbiology Laboratory, Public Health Agency of Canada, Canada}
\affil[5]{The Pioneer Centre for SMARTbiomed, Big Data Institute, Li Ka Shing Centre for Health Information and Discovery, University of Oxford, United Kingdom}
\affil[6]{Department of Zoology and Biodiversity Research Centre, University of British Columbia, Vancouver BC Canada}

\affil[7]{Joint second author}
\affil[8]{Lead contact}

%%%  List only one email address per corresponding author.

\affil[*]{Correspondence: shing.zhan@ndph.ox.ac.uk}
\affil[**]{Correspondence: jerome.kelleher@bdi.ox.ac.uk}

@@

Ancestral recombination graphs (ARGs) describe the reticulate 
genealogies of sampled sequences in a recombining species\cite{Wong2024},
and provide a natural and efficient means of 
systematically incorporating recombination 
into the study of SARS-CoV-2.
While ARGs have been of theoretical interest in population genetics 
for several decades\cite{Hudson1983,Griffiths1991two,Griffiths1997ancestral},
recent breakthroughs in
simulation\cite{Kelleher2016,Kelleher2018efficient,Haller2019,Gopalan2025bridging}
and inference~\citep{Rasmussen2014,Speidel2019,Kelleher2019,
Wohns2022,Zhang2023,Gunnarsson2024,Deng2025robust} have led to a surge 
of interest in their application in population and statistical 
genetics\cite{Brandt2024,Lewanski2024,Nielsen2025}.
% This is necessary because a bunch of the phylo literature refers
% to ARGs, but it's all in the "coalescent with recombination" sense
% Rannala2025 dismisses ARG-based methods at a stroke because they're
% all based on the assumption of a single panmictic population 
As the range of applications for ARGs has broadened, the term has itself evolved from a specific model of coalescence with 
recombination  \cite{Hudson1983,Griffiths1997ancestral}to a rich data structure representing recombinant ancestry\cite{Minichiello2006mapping,Wong2024}.
The development of extensive software support has facilitated the broader application of ARGS. In particular, the collaboratively built tskit library~\cite{Ralph2020} underpins a 
rapidly growing software ecosystem of
simulation~\cite{Baumdicker2022,Haller2019,Petr2023,Tsambos2023link,Tagami2024tstrait},
visualisation~\cite{Karthikeyan2025tsbrowse,Kitchens2025tskit,Talbot2025argscape},
inference~\cite{Kelleher2019,Wohns2022,Mahmoudi2022,Martin2025model,Pieszko2025detecting}
% More here? I'm sure there's others
and data analysis~\cite{Fan2022,Nowbandegani2023extremely,Fritze2024forest}
tools.

@@

%%%  All original research papers must include a
%%%  comprehensive and accurate ``data and code
%%%  availability'' statement within the ``resource
%%%  availability'' component of the paper before it
%%%  is accepted for publication. These statements
%%%  are structured and consist of three bulleted
%%%  components. Each component must be present.
\begin{itemize}

\item The ARG in tskit format has been deposited at Zenodo and is publicly
available at \url{https://zenodo.org/records/17558489}. The UShER tree
in tskit format is also available, as well as the intersection files.
\item The sequences alignments in VCF Zarr format have been deposited at 
Zenodo and are publicly available at \url{https://zenodo.org/records/16314739}.
\item The Snakemake workflow for aligning and converting the Viridian v05 dataset to VCF Zarr is publicly available at \url{https://github.com/jeromekelleher/sc2ts-paper/blob/main/viridian\_dataset/}.
\item The complete configuration file for running sc2ts to build the ARG above is 
publicly available at \url{https://github.com/jeromekelleher/sc2ts-paper/blob/main/inference/viridian\_config.toml}.
\item The Snakemake workflow for ARG post-processing is publicly 
available at \url{https://github.com/jeromekelleher/sc2ts-paper/blob/main/arg_postprocessing/Snakefile}.
\item The original code of sc2ts is publicly available on 
GitHub at \url{https://github.com/tskit-dev/sc2ts}.
\item The Jupyter notebooks and the Mathematica script to perform the analyses in this paper are publicly available on GitHub at \url{https://github.com/jeromekelleher/sc2ts-paper/}.
\end{itemize}

@@

% Credit system: https://credit.niso.org/
Conceptualization, SHZ, SPO, JK;
% Methodology, software, resources, visualization
methodology, SHZ, YW, AI, KE, BJ, DSP, SPO, JK;
% Invesigation, data curation, formal analysis, validation
investigation, SHZ, YW, AI, KE, IG, SPO, JK;
writing--original draft, SHZ, JK;
writing--review \& editing, SHZ, YW, AI, KE, IG, BJ, DSP, CLM, SPO, JK;
resources, JK;
supervision, JK;
funding acquisition, JK.

@@

% \section*{SUPPLEMENTAL INFORMATION INDEX}

% %%%  Supplemental information must be uploaded as
% %%%  separate files. In the main text, please list the
% %%%  files to be included in a brief index. For details,
% %%%  please review the supplemental information guidelines:

% %%%  Journals with STAR Methods:
% %%%  https://www.cell.com/STAR-supplemental-information

% \begin{description}
%   \item Figures S1-SX and their legends in a PDF
%   \item Table S1. A descriptive title for an Excel file that was too large to appear in the PDF
% \end{description}

% \newpage

% \section*{MAIN FIGURE TITLES AND LEGENDS}

% %%%  At final submission, figure files MUST be
% %%%  provided separately as high-resolution image
% %%%  files. All of the panels for a figure should
% %%%  be in the same file. Figures should have
% %%%  clear labels/file names (Figure 1, Figure 2,
% %%%  etc.).

% %%%  Figure titles and legends should be placed
% %%%  at the end of the main text. You do not
% %%%  need to place the figures, nor their titles
% %%%  and legends, within the main text. While
% %%%  typesetting your article, our team will
% %%%  place each figure in the best location
% %%%  based on the final layout and on your
% %%%  figure citations, e.g., (Figures 1A and 1B).

% %%%  Please review the figure guidelines before
% %%%  submitting your final materials:
% %%%  https://www.cell.com/figureguidelines.

% \noindent\includegraphics[width=0.85\linewidth]{Figure1.jpg}

% \subsection*{Figure 1. A brief title that describes the entire figure without citing specific panels}

% The figure legend can be all one paragraph and describe the images (A), graphs (B), and plots (C), etc., together.
% \newline
% (A) Or each panel or group of panels can be described separately, as shown here and below.
% \newline
% (B) Graph of X, Y, and Z.
% \newline
% (C and D) If panels are grouped like this, please explicitly describe each panel, e.g., ``Images showing SEM (C) and TEM (D).''
% \newline
% Please define all scale and error bars, and please review the Cell Press figure guidelines before submission: \href{https://www.cell.com/figureguidelines}{https://www.cell.com/figureguidelines}. Example figure created by Cassie Comeau, Cell Press.

% \newpage

% \section*{MAIN TABLES, INCLUDING TITLES AND LEGENDS}

% %%%  Whenever possible, we encourage you to submit
% %%%  your main-text tables as Microsoft Word documents,
% %%%  using Word's table function. This will ensure
% %%%  the best results during conversion. Tables
% %%%  should be numbered Table 1, Table 2, etc. and
% %%%  should not include subpanels (do not use Table 1A,
% %%%  1B, etc.). Give each table a brief descriptive
% %%%  title. Table legends are optional but encouraged.
% %%%  Footnotes (superscript lowercase letters) should
% %%%  be used where necessary to indicate some feature
% %%%  of the data; please do not use bold, italic,
% %%%  coloured text, or shading for this purpose. Use
% %%%  separate cells, not line breaks or spaces, for
% %%%  all discrete data elements. Small embedded
% %%%  graphics with colour are OK.

% %%%  Like figures, all tables must be cited within
% %%%  the main text, and our typesetting team will
% %%%  place the tables within the typeset paper at
% %%%  the appropriate locations.

% \subsection*{Table 1. A table with clear organization of data}

% \begin{tabular}{|l | l | l | l|}
%  \hline
%  \textbf{Column 1} & \textbf{Column 2} & \textbf{Column 3} & \textbf{Column 4} \\ [1ex]
%  \hline
%  Row A\textsuperscript{a} & 6 & 87,837 & 787 \\ [1ex]
%  \hline
%  Row B & 7 & 78 & 5,415 \\ [1ex]
%  \hline
%  Row C & 545 & 778 & 7507 \\ [1ex]
%  \hline
%  Row D & 545 & 18,744 & 7,560 \\ [1ex]
%  \hline
%  Row E & 88 & 788 & 6,344 \\ [1ex]
%  \hline
% \end{tabular}

% \bigskip

% The table legend (optional) follows the table itself.
% The legend should be used to provide additional info that relates to the table as a whole.

% \textsuperscript{a}Footnotes can be used to provide additional info on specific content within the table,
% such as this footnote to the first row (row A). Do not use footnotes in the table title.

% \textsuperscript{b}More footnotes

%%%  REFERENCES: As of 2023, all Cell Press journals
%%%  use Numbered (AMA) style. We recommend placing
%%%  your references in the included "references.bib"
%%%  file.

\bibliography{references}

@@

%%%  In your References, please include only articles
%%%  that are published (online publication and
%%%  preprint servers are OK). Unpublished data,
%%%  submitted and/or accepted manuscripts, abstracts,
%%%  and personal communications should be cited within
%%%  the text only ("unpublished data," "data not
%%%  shown," "Alice Smith, personal communication")
%%%  and not included in the references list. Personal
%%%  communication should be documented by a letter
%%%  of permission. Whenever possible, please make
%%%  sure your .bib file has the complete author lists
%%%  for each item (at minimum, the first 11 authors
%%%  listed).

%%% All Cell Press \textbf{life and medical science} journals, and the multidisciplinary journal \textbf{iScience},
%%% use the \textbf{\href{https://www.cell.com/star-authors-guide}{STAR Methods}} format for reporting materials and methods.

%%% If you are publishing in a STAR Methods journal, please refer to the appropriate guide for authors:
%%% Cell authors should download the guide https://www.cell.com/pb-assets/journals/research/cell/methods/Methods_Guide_Cell-1678470557763.pdf.

@@

\FloatBarrier

>>>>

% Use the basic LaTeX article class, 12pt text
\documentclass[12pt]{article}

% Science uses Times font. If you don't have this installed (most LaTeX installations will be
% fine) or prefer the old Computer Modern fonts, comment out the following line
% \usepackage{newtxtext,newtxmath}
% Depending on your LaTeX fonts installation, you might get better results with one or both of these:
%\usepackage{mathptmx}
%\usepackage{txfonts}

% Allow external graphics files
\usepackage{graphicx}

% Use US letter sized paper with 1 inch margins
\usepackage[letterpaper,margin=1in]{geometry}

% Double line spacing, including in captions
\linespread{1.5} % For some reason double spacing is 1.5, not 2.0!

% One space after each sentence
\frenchspacing

% Abstract formatting and spacing - no heading
\renewenvironment{abstract}
	{\quotation}
	{\endquotation}

% No date in the title section
\date{}

% Reference section heading
\renewcommand\refname{References and Notes}

% Figure and Table labels in bold
\makeatletter
\renewcommand{\fnum@figure}{\textbf{Figure \thefigure}}
\renewcommand{\fnum@table}{\textbf{Table \thetable}}
\makeatother

% Call the accompanying scicite.sty package.
% This formats citation numbers in Science style.
\usepackage{scicite}

% Provides the \url command, and fixes a crash if URLs or DOIs contain underscores
\usepackage{url}

%%%%%%%%%%%% CUSTOM COMMANDS AND PACKAGES %%%%%%%%%%%%

\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{amssymb}
\usepackage[hypertexnames=false]{hyperref}

\graphicspath{{../figures}}

% Authors can define simple custom commands e.g. as shortcuts to save on typing
% Use \newcommand (not \def) to avoid overwriting existing commands.
% Keep them as simple as possible and note the warning in the text below.
% Example:
\newcommand{\pcc}{\,cm$^{-3}$}	% per cm-cubed

% Please DO NOT import additional external packages or .sty files.
% Those are unlikely to work with our conversion software and will cause problems later.
% Don't add any more \usepackage{} commands.

%%%%%%%%%%%%%%%% TITLE AND AUTHORS %%%%%%%%%%%%%%%%

% Title of the paper.
% Keep it short and understandable by any reader of Science.
% Avoid acronyms or jargon. Use sentence case.
\def\scititle{
A Pandemic-Scale Ancestral Recombination Graph for SARS-CoV-2
}
% Store the title in a variable for reuse in the supplement (otherwise \maketitle deletes it)
\title{\bfseries \boldmath \scititle}

% Author and institution list.
% Institution numbers etc. should be hard-coded, do *not* use the \footnote command.
\author{
	% You can write out first names or use initials - either way is acceptable, but be consistent
	First~Author$^{1\ast\dagger}$,
	A.~Scientist$^{2\dagger}$,
	Someone~E.~Else$^{2}$\and
	% Additional lines of authors should be inserted using the \and command (not \\)
	% Institution list, in a slightly smaller font
	\small$^{1}$Department, Institution, City \& Postal Code, Country.\and
	\small$^{2}$Another Department, Different Institution, City \& Postal Code, Country.\and
	% Identify at least one corresponding author, with contact email address
	\small$^\ast$Corresponding author. Email: example@mail.com\and
	% Joint contributions can be indicated like this
	\small$^\dagger$These authors contributed equally to this work.
}

\date{}

% \author[1,2,8,*,\orcidlink{0000-0002-6351-8873}]{Shing~H.~Zhan}
% \author[1,7,\orcidlink{0000-0002-3536-6411}]{Yan~Wong}
% \author[3,7,\orcidlink{0000-0001-6402-9396}]{Anastasia~Ignatieva}
% \author[4,\orcidlink{0000-0001-6862-7756}]{Katherine~Eaton}
% \author[1,\orcidlink{0000-0002-3547-7226}]{Isobel~Guthrie}
% \author[1,\orcidlink{0000-0002-1982-6801}]{Benjamin~Jeffery}
% \author[1,3,5,\orcidlink{0000-0002-0824-0047}]{Duncan~S.~Palmer}
% \author[4,\orcidlink{0000-0002-1543-4501}]{Carmen~Lia~Murall}
% \author[6,\orcidlink{0000-0003-3042-0818}]{Sarah~P.~Otto}
% \author[1,**,\orcidlink{0000-0002-7894-5253}]{Jerome~Kelleher}

% %%%  Institutional affiliations should contain the
% %%%  following information at minimum: department(s)/
% %%%  subunit(s), institution, city, state/region (if
% %%%  applicable), and country.

% \affil[1]{Big Data Institute, Li Ka Shing Centre for Health
% Information and Discovery, University of Oxford, United Kingdom}
% \affil[2]{Infectious Disease Epidemiology Unit (IDEU), Nuffield Department of Population Health, University of Oxford, Oxford, United Kingdom}
% \affil[3]{Department of Statistics, University of Oxford, United Kingdom}
% \affil[4]{National Microbiology Laboratory, Public Health Agency of Canada, Canada}
% \affil[5]{The Pioneer Centre for SMARTbiomed, Big Data Institute, Li Ka Shing Centre for Health Information and Discovery, University of Oxford, United Kingdom}
% \affil[6]{Department of Zoology and Biodiversity Research Centre, University of British Columbia, Vancouver BC Canada}

% \affil[7]{Joint second author}
% \affil[8]{Lead contact}

% %%%  List only one email address per corresponding author.

% \affil[*]{Correspondence: shing.zhan@ndph.ox.ac.uk}
% \affil[**]{Correspondence: jerome.kelleher@bdi.ox.ac.uk}

@@

Ancestral recombination graphs (ARGs) describe the reticulate 
genealogies of sampled sequences in a recombining species\cite{Wong2024},
and provide a natural and efficient means of 
systematically incorporating recombination 
into the study of SARS-CoV-2.
While ARGs have been of theoretical interest in population genetics 
for several decades\cite{Hudson1983,Griffiths1991two,Griffiths1997ancestral},
recent breakthroughs in
simulation\cite{Kelleher2016,Kelleher2018efficient,Haller2019,Gopalan2025bridging}
and inference~\cite{Rasmussen2014,Speidel2019,Kelleher2019,
Wohns2022,Zhang2023,Gunnarsson2024,Deng2025robust} have led to a surge 
of interest in their application in population and statistical 
genetics\cite{Brandt2024,Lewanski2024,Nielsen2025}.
% This is necessary because a bunch of the phylo literature refers
% to ARGs, but it's all in the "coalescent with recombination" sense
% Rannala2025 dismisses ARG-based methods at a stroke because they're
% all based on the assumption of a single panmictic population 
As the range of applications for ARGs has broadened, the term has itself evolved from a specific model of coalescence with 
recombination  \cite{Hudson1983,Griffiths1997ancestral}to a rich data structure representing recombinant ancestry\cite{Minichiello2006mapping,Wong2024}.
The development of extensive software support has facilitated the broader application of ARGS. In particular, the collaboratively built tskit library~\cite{Ralph2020} underpins a 
rapidly growing software ecosystem of
simulation~\cite{Baumdicker2022,Haller2019,Petr2023,Tsambos2023link,Tagami2024tstrait},
visualisation~\cite{Karthikeyan2025tsbrowse,Kitchens2025tskit,Talbot2025argscape},
inference~\cite{Kelleher2019,Wohns2022,Mahmoudi2022,Martin2025model,Pieszko2025detecting}
% More here? I'm sure there's others
and data analysis~\cite{Fan2022,Nowbandegani2023extremely,Fritze2024forest}
tools.

@@

%%%  All original research papers must include a
%%%  comprehensive and accurate ``data and code
%%%  availability'' statement within the ``resource
%%%  availability'' component of the paper before it
%%%  is accepted for publication. These statements
%%%  are structured and consist of three bulleted
%%%  components. Each component must be present.
\begin{itemize}
\item The ARG in tskit format has been deposited at Zenodo and is publicly
available at \url{https://zenodo.org/records/17558489}. The UShER tree
in tskit format is also available, as well as the intersection files.
\item The sequences alignments in VCF Zarr format have been deposited at 
Zenodo and are publicly available at \url{https://zenodo.org/records/16314739}.
\item The Snakemake workflow for aligning and converting the Viridian v05 dataset to VCF Zarr is publicly available at \url{https://github.com/jeromekelleher/sc2ts-paper/blob/main/viridian\_dataset/}.
\item The complete configuration file for running sc2ts to build the ARG above is 
publicly available at \url{https://github.com/jeromekelleher/sc2ts-paper/blob/main/inference/viridian\_config.toml}.
\item The Snakemake workflow for ARG post-processing is publicly 
available at \url{https://github.com/jeromekelleher/sc2ts-paper/blob/main/arg_postprocessing/Snakefile}.
\item The original code of sc2ts is publicly available on 
GitHub at \url{https://github.com/tskit-dev/sc2ts}.
\item The Jupyter notebooks and the Mathematica script to perform the analyses in this paper are publicly available on GitHub at \url{https://github.com/jeromekelleher/sc2ts-paper/}.
\end{itemize}

@@

% Credit system: https://credit.niso.org/
Conceptualization, SHZ, CLM, SPO, JK;
% Methodology, software, resources, visualization
methodology, SHZ, YW, AI, KE, BJ, DSP, SPO, JK;
% Invesigation, data curation, formal analysis, validation
investigation, SHZ, YW, AI, KE, IG, SPO, JK;
writing--original draft, SHZ, JK;
writing--review \& editing, SHZ, YW, AI, KE, IG, BJ, DSP, CLM, SPO, JK;
resources, JK;
supervision, JK;
funding acquisition, JK.

@@

%%%%%%%%%%%%%%%% REFERENCES %%%%%%%%%%%%%%%

\clearpage % Clear all remaining figures and tables then start a new page

% The list of references goes after the main text and before the acknowledgements
% When preparing an initial submission, we recommend you use BibTeX, like this:
%
\bibliography{references} % for a file named science_template.bib
\bibliographystyle{sciencemag}

@@

%%%%%%%%%%%%%%%% ACKNOWLEDGEMENTS %%%%%%%%%%%%%%%

\section*{Acknowledgments}
Here you can thank helpful colleagues who did not meet the journal's authorship criteria, or
provide other acknowledgements that don't fit the (compulsory) subheadings below.
Formatting requirements for each of these sections differ between the \textit{Science}-family
journals; consult the instructions to authors on the journal website for full details.
\paragraph*{Funding:}
List the grants, fellowships etc. that funded the research;
use initials to specify which author(s) were supported by each source.
Include grant numbers when appropriate or required by the funding agency.
For example: F.~A. was funded by the Generous Science Agency grant~2372.
\paragraph*{Author contributions:}
List each author’s contributions to the paper.
Use initials to abbreviate author names.
\paragraph*{Competing interests:}
Disclose any potential conflicts of interest for all authors, such as patent applications,
additional affiliations, consultancies, financial relationships etc.
See the journal editorial policies web page for types of competing interest that must be declared.
If there are no competing interests, state:
``There are no competing interests to declare.''
\paragraph*{Data and materials availability:}
Specify where the data, software, physical samples, simulation outputs or other materials
underlying the paper are archived.
They must be publicly accessible when the paper is published (without embargo) and enable
readers to reproduce all the results in the paper.
Contact the editor if you’re unsure what needs to be shared.

Our preference is for digital material to be deposited in a suitable non-profit online data or
software repository that issues the material with a DOI.
Alternatively, an institutional repository, subject-based archive, commercial repository etc.
is acceptable, as are (short) supplementary tables or a machine-readable supplementary data file.
‘Available on request’ or personal web pages are not allowed.

Cite the relevant DOI \cite{dataset}, URL \cite{example_url} or reference \cite{example2}
in this statement.
These \textit{do not} count towards the reference limit if they are only cited in the acknowledgements.
Be specific and state a unique identifier -- such as an accession number, software version number
or observation ID -- so readers can easily retrieve the exact material used.

Declare any restrictions on sharing or re-use -- such as a Materials Transfer Agreement (MTA) or
legal restrictions -- which must be approved by your editor.
Unreasonable restrictions will preclude publication.
Consult the journal's editorial policies web page for more details.

@@

% \FloatBarrier
